The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-03-21 manuscript/manuscript.tex
Before "git pull" from overleaf

\section{discussion}
\label{sec:dis}
\subsection{Systematic error}
In our analysis, we adopt one stellar population to the overall sample. We note that adopting the private stellar populations for these samples which have both multi-band host magnitude could be more robust in principle. However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost. Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry. \textcolor{red}{Describe the ground-based data}. In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host relations. The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.

\subsection{Comparison to the inactive galaxies}
To understand whether AGNs activity affects their galaxies' morphology, we compared the 32 host measurements to the inactive galaxies in CANDLES imaging survey. We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) from the CANDLES-COSMOS catalog. Their \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.

\textcolor{blue}{ Description and comments to be written}:
We show the \smass-\Reff\ relations and \smass-\sersic\ n in Figure~\ref{fig:Mstar-rn}. 
The comparison the histogram of \Reff\ and \sersic\ n are shown in Figure~\ref{fig:hist_rn}.

@@

\section*{Acknowledgments}
We thank the people who discuss with the paper.

@@

\begin{deluxetable*}{ccccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The host inference of CID1174} 
\tablehead{ 
\colhead{PSF rank} &
\colhead{total $\chi ^2$} & 
\colhead{weights $w_i$} &
\colhead{host flux (counts)} &
\colhead{host flux ratio}&
\colhead{\Reff (arcsec)}&
\colhead{\sersic\ $n$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
1 & $8584.429$ & $1.000$ & $82.209$ & $35.4\%$ & $0\farcs{}345$ & $1.11$ \\
2 & $8646.711$ & $0.920$ & $99.102$ & $41.9\%$ & $0\farcs{}298$ & $1.93$ \\
3 & $8816.947$ & $0.734$ & $76.74$ & $33.0\%$ & $0\farcs{}365$ & $1.10$ \\
4 & $9304.841$ & $0.383$ & $128.618$ & $54.7\%$ & $0\farcs{}231$ & $2.78$ \\
5 & $9652.575$ & $0.241$ & $187.498$ & $79.0\%$ & $0\farcs{}116$ & $6.18$ \\
6 & $9917.101$ & $0.170$ & $100.166$ & $42.3\%$ & $0\farcs{}287$ & $2.07$ \\
7 & $10018.324$ & $0.148$ & $75.061$ & $32.3\%$ & $0\farcs{}365$ & $1.23$ \\
8 & $10087.456$ & $0.135$ & $79.835$ & $34.3\%$ & $0\farcs{}358$ & $1.20$ \\
\hline\\
Weighted value & & & $97.322\pm28.336$ & $41.5\%\pm11.7\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.86\pm1.26$  \\
\enddata
\label{tab:weight_CID1174}
\tablecomments{
Column~1: Rank of the PSF from the library.
Column~2: Total $\chi ^2$ for the corresponding PSF.
Column~3: Weights for the inference.
Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
For this sample, the inflation parameter $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
}
\end{deluxetable*}

@@

@@

CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13\substack{+0.09\\-0.07}$ &$10.85\substack{+0.14\\-0.12}$\\
CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49\substack{+0.09\\-0.07}$ &$10.21\substack{+0.13\\-0.12}$\\
CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95\substack{+0.32\\-0.14}$ &$10.66\substack{+0.34\\-0.18}$\\
CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13\substack{+0.02\\-0.02}$ &$10.85\substack{+0.1\\-0.1}$\\
CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26\substack{+0.07\\-0.05}$ &$10.98\substack{+0.12\\-0.11}$\\
CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17\substack{+0.09\\-0.07}$ &$10.89\substack{+0.14\\-0.12}$\\
CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25\substack{+0.09\\-0.07}$ &$10.97\substack{+0.13\\-0.12}$\\
CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07\substack{+0.01\\-0.01}$ &$10.79\substack{+0.1\\-0.1}$\\
CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21\substack{+0.02\\-0.02}$ &$10.93\substack{+0.1\\-0.1}$\\
CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19\substack{+0.02\\-0.02}$ &$10.91\substack{+0.1\\-0.1}$\\
CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15\substack{+0.22\\-0.12}$ &$10.87\substack{+0.24\\-0.16}$\\
CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79\substack{+0.1\\-0.07}$ &$10.51\substack{+0.14\\-0.12}$\\
CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81\substack{+0.14\\-0.09}$ &$10.53\substack{+0.17\\-0.13}$\\
CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10\substack{+0.14\\-0.09}$ &$10.82\substack{+0.18\\-0.14}$\\
CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07\substack{+0.08\\-0.06}$ &$10.79\substack{+0.13\\-0.12}$\\
LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40\substack{+0.05\\-0.05}$ &$11.12\substack{+0.11\\-0.11}$\\
LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21\substack{+0.06\\-0.05}$ &$10.93\substack{+0.11\\-0.11}$\\
LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17\substack{+0.04\\-0.03}$ &$10.88\substack{+0.11\\-0.1}$\\
XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98\substack{+0.04\\-0.04}$ &$10.70\substack{+0.11\\-0.11}$\\
XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24\substack{+0.08\\-0.06}$ &$10.96\substack{+0.13\\-0.12}$\\
XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20\substack{+0.16\\-0.1}$ &$10.92\substack{+0.19\\-0.14}$\\
CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.80\substack{+0.1\\-0.07}$ &$10.52\substack{+0.14\\-0.12}$\\
CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.98\substack{+0.04\\-0.03}$ &$10.70\substack{+0.11\\-0.1}$\\
CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ... & ... & ... & $11.61\substack{+0.18\\-0.11}$ &$11.33\substack{+0.2\\-0.15}$\\
CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.14\substack{+0.15\\-0.1}$ &$9.86\substack{+0.18\\-0.14}$\\
ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ... & ... & ... & $11.25\substack{+0.08\\-0.06}$ &$10.97\substack{+0.13\\-0.12}$\\
SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ... & ... & ... & $10.84\substack{+0.06\\-0.05}$ &$10.56\substack{+0.12\\-0.11}$\\
SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.89\substack{+0.07\\-0.05}$ &$10.61\substack{+0.12\\-0.11}$\\
SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ... & ... & ... & $10.86\substack{+0.05\\-0.04}$ &$10.58\substack{+0.11\\-0.11}$\\
SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ... & ... & ... & $11.28\substack{+0.08\\-0.06}$ &$11.00\substack{+0.13\\-0.12}$\\
SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $10.03\substack{+0.29\\-0.14}$ &$9.75\substack{+0.31\\-0.17}$\\
SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ... & ... & ... & $11.12\substack{+0.13\\-0.09}$ &$10.83\substack{+0.16\\-0.13}$\\

@@

\begin{figure*}
\centering
{
\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
}
\caption{\label{fig:hist_compare} 
Comparison of the histogram of the inferred host flux ratio, based on the different amount of the top-ranked PSFs.}
\end{figure*}

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-L_ev.pdf}}\\
\end{tabular}
\caption{\label{fig:ML} 
Observed \mbh-\lhost\ relation (left), evolution-corrected relation (right).}
\end{figure*}

\begin{figure}
\centering
{
\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}
}
\caption{\label{fig:ML-vz} 
The offset as a function of redshift.}
\end{figure}

>>>>

\section{discussion}
\label{sec:dis}
\subsection{Systematic error}

In our analysis, we adopt one stellar population to the overall sample. We note that adopting the private stellar populations for these samples which have both multi-band host magnitude could be more robust in principle. However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost. Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry. \textcolor{red}{Describe the ground-based data}. In this paper, we focus on the decomposing of the AGN and carry out a rapid analysis of the \mbh-host relations. The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.

\subsection{Comparison to the inactive galaxies}
We compared the morphology of AGNs host galaxies to the inactive galaxies in CANDLES imaging survey. We select 4401 inactive galaxies in a comparable redshift range ($1.2<z<1.7$) whose \sersic\ properties are inferred by \citet{VDwel++2012} by \galfit, and their stellar masses are derived by 3-D-HST spectroscopic survey \citep{Momcheva2016, Brammer2012}.

In Figure~\ref{fig:Mstar-rn}, we plot the \smass\ versus the \Reff\ and \sersic\ index. The color coding is based on the filter flux ratio between WFC3 and ACS. The distribution of \smass-\Reff\ relation show that our AGN hosts concentrate at the high end of the stellar mass, close to the red sequence.

We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value. We perform the Kolmogorov?Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively.

@@

\section*{Acknowledgments}
Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. These observations are associated with programs
\#15115.

The authors fully appreciate the discussions with Vardha N. Bennert, Takahiro Morishita.

SB, TT and AJS acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.

This work has made use of lenstronomy \citep{lenstronomy}, Astropy \citep{Astropy}, photutils, TOPCAT \citep{TOPCAT}, Matplotlib \citep{Matplotlib} and standard Python libraries.

@@

\begin{deluxetable*}{ccccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The host inference of CID1174} 
\tablehead{ 
\colhead{PSF rank} &
\colhead{total $\chi ^2$} & 
\colhead{weights $w_i$} &
\colhead{host flux (counts)} &
\colhead{host flux ratio}&
\colhead{\Reff (arcsec)}&
\colhead{\sersic\ $n$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
1 & $8584.429$ & $1.000$ & $82.2$ & $35\%$ & $0\farcs{}345$ & $1.1$ \\
2 & $8646.711$ & $0.920$ & $99.1$ & $42\%$ & $0\farcs{}298$ & $1.9$ \\
3 & $8816.947$ & $0.734$ & $76.7$ & $33\%$ & $0\farcs{}365$ & $1.1$ \\
4 & $9304.841$ & $0.383$ & $128.6$ & $55\%$ & $0\farcs{}231$ & $2.8$ \\
5 & $9652.575$ & $0.241$ & $187.5$ & $79\%$ & $0\farcs{}116$ & $6.2$ \\
6 & $9917.101$ & $0.170$ & $100.2$ & $42\%$ & $0\farcs{}287$ & $2.1$ \\
7 & $10018.324$ & $0.148$ & $75.1$ & $32\%$ & $0\farcs{}365$ & $1.2$ \\
8 & $10087.456$ & $0.135$ & $79.8$ & $34\%$ & $0\farcs{}358$ & $1.2$ \\
\hline\\
Weighted value & & & $97.322\pm28.336$ & $42\%\pm12\%$& $0\farcs{}309\pm0\farcs{}065$  & $1.9\pm1.3$  \\
\enddata
\label{tab:weight_CID1174}
\tablecomments{
Column~1: Rank of the PSF from the library.
Column~2: Total $\chi ^2$ for the corresponding PSF.
Column~3: Weights for the inference.
Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
For this sample, the inflation parameter $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
}
\end{deluxetable*}

@@

\setlength{\tabcolsep}{20pt}
\renewcommand{\arraystretch}{1.5}

@@

CID1174 & $2.307$ & $42\%\pm12\%$ & $0\farcs{}31\pm0\farcs{}07$ & $1.9\pm1.3$ & $21.48\substack{+0.37\\-0.28}$ & $2.496$ & $11\%\pm1\%$ & $23.21\substack{+0.11\\-0.10}$ & $11.13\substack{+0.15\\-0.11}$ &$10.85\substack{+0.18\\-0.15}$\\[3pt]
CID1281 & $1.322$ & $49\%\pm14\%$ & $0\farcs{}24\pm0\farcs{}09$ & $3.2\pm1.5$ & $22.88\substack{+0.36\\-0.27}$ & $1.378$ & $19\%\pm8\%$ & $24.83\substack{+0.60\\-0.38}$ & $10.49\substack{+0.15\\-0.11}$ &$10.21\substack{+0.18\\-0.15}$\\[3pt]
CID206 & $2.054$ & $35\%\pm24\%$ & $0\farcs{}29\pm0\farcs{}15$ & $3.1\pm2.5$ & $21.82\substack{+1.30\\-0.58}$ & $1.903$ & $8\%\pm2\%$ & $23.67\substack{+0.40\\-0.29}$ & $10.95\substack{+0.52\\-0.23}$ &$10.66\substack{+0.53\\-0.25}$\\[3pt]
CID216 & $1.514$ & $94\%\pm5\%$ & $0\farcs{}25\pm0\farcs{}06$ & $6.2\pm1.2$ & $21.51\substack{+0.05\\-0.05}$ & $1.425$ & $35\%\pm2\%$ & $23.45\substack{+0.05\\-0.05}$ & $11.13\substack{+0.03\\-0.03}$ &$10.85\substack{+0.10\\-0.10}$\\[3pt]
CID237 & $2.349$ & $30\%\pm6\%$ & $0\farcs{}87\pm0\farcs{}17$ & $4.7\pm1.7$ & $21.28\substack{+0.26\\-0.21}$ & $2.354$ & $3\%\pm2\%$ & $23.72\substack{+1.04\\-0.52}$ & $11.26\substack{+0.11\\-0.09}$ &$10.98\substack{+0.14\\-0.13}$\\[3pt]
CID255 & $1.625$ & $19\%\pm5\%$ & $0\farcs{}19\pm0\farcs{}06$ & $4.2\pm1.5$ & $21.61\substack{+0.37\\-0.28}$ & 2.858 & $4\%\pm2\%$ & $22.89\substack{+0.60\\-0.39} $& $11.17\substack{+0.15\\-0.11}$ &$10.89\substack{+0.18\\-0.15}$\\[3pt]
CID3242 & $2.751$ & $46\%\pm13\%$ & $0\farcs{}20\pm0\farcs{}16$ & $6.1\pm1.9$ & $21.16\substack{+0.35\\-0.26}$ & $2.596$ & $5\%\pm1\%$ & $23.60\substack{+0.34\\-0.26}$ & $11.25\substack{+0.14\\-0.11}$ &$10.97\substack{+0.17\\-0.15}$\\[3pt]
CID3570 & $1.665$ & $77\%\pm2\%$ & $0\farcs{}70\pm0\farcs{}01$ & $0.7\pm0.1$ & $21.16\substack{+0.02\\-0.02}$ & $1.332$ & $86\%\pm2\%$ & $22.97\substack{+0.01\\-0.01}$ & $11.07\substack{+0.02\\-0.02}$ &$10.79\substack{+0.10\\-0.10}$\\[3pt]
CID452 & $1.684$ & $75\%\pm4\%$ & $0\farcs{}37\pm0\farcs{}02$ & $1.4\pm0.2$ & $21.18\substack{+0.06\\-0.06}$ & $1.452$ & $38\%\pm1\%$ & $22.73\substack{+0.02\\-0.02}$ & $11.21\substack{+0.03\\-0.03}$ &$10.93\substack{+0.10\\-0.10}$\\[3pt]
CID454 & $2.203$ & $36\%\pm3\%$ & $0\farcs{}39\pm0\farcs{}02$ & $0.6\pm0.1$ & $21.20\substack{+0.08\\-0.07}$ & $1.291$ & $9\%\pm1\%$ & $23.35\substack{+0.06\\-0.06}$ & $11.19\substack{+0.04\\-0.04}$ &$10.91\substack{+0.10\\-0.10}$\\[3pt]
CID50 & $5.576$ & $17\%\pm9\%$ & $0\farcs{}16\pm0\farcs{}11$ & $3.2\pm2.2$ & $20.93\substack{+0.86\\-0.48}$ & $4.940$ & $5\%\pm3\%$ & $22.50\substack{+1.15\\-0.55}$ & $11.15\substack{+0.35\\-0.19}$ &$10.87\substack{+0.36\\-0.21}$\\[3pt]
CID543 & $1.902$ & $31\%\pm10\%$ & $0\farcs{}10\pm0\farcs{}00$ & $0.5\pm0.3$ & $21.99\substack{+0.41\\-0.30}$ & $1.435$ & $5\%\pm2\%$ & $23.77\substack{+0.53\\-0.36}$ & $10.79\substack{+0.16\\-0.12}$ &$10.51\substack{+0.19\\-0.15}$\\[3pt]
CID597 & $1.565$ & $42\%\pm17\%$ & $0\farcs{}17\pm0\farcs{}06$ & $1.8\pm0.8$ & $21.87\substack{+0.54\\-0.36}$ & $1.254$ & $12\%\pm1\%$ & $23.56\substack{+0.13\\-0.11}$ & $10.81\substack{+0.22\\-0.15}$ &$10.53\substack{+0.24\\-0.18}$\\[3pt]
CID607 & $1.692$ & $44\%\pm18\%$ & $0\farcs{}21\pm0\farcs{}09$ & $3.4\pm1.1$ & $21.19\substack{+0.58\\-0.37}$ & $2.590$ & $5\%\pm2\%$ & $23.57\substack{+0.51\\-0.35}$ & $11.10\substack{+0.23\\-0.15}$ &$10.82\substack{+0.25\\-0.18}$\\[3pt]
CID70 & $2.041$ & $20\%\pm5\%$ & $0\farcs{}42\pm0\farcs{}10$ & $3.6\pm1.0$ & $21.86\substack{+0.30\\-0.24}$ & $2.361$ & $2\%\pm1\%$ & $24.63\substack{+0.68\\-0.41}$ & $11.07\substack{+0.12\\-0.10}$ &$10.79\substack{+0.16\\-0.14}$\\[3pt]
LID1273 & $1.697$ & $53\%\pm9\%$ & $0\farcs{}30\pm0\farcs{}04$ & $1.2\pm0.5$ & $20.94\substack{+0.21\\-0.18}$ & $2.137$ & $6\%\pm1\%$ & $23.29\substack{+0.15\\-0.13}$ & $11.40\substack{+0.09\\-0.07}$ &$11.12\substack{+0.13\\-0.12}$\\[3pt]
LID1538 & $2.362$ & $44\%\pm8\%$ & $0\farcs{}18\pm0\farcs{}04$ & $2.8\pm0.5$ & $21.25\substack{+0.22\\-0.18}$ & $2.173$ & $8\%\pm1\%$ & $23.09\substack{+0.19\\-0.16}$ & $11.21\substack{+0.09\\-0.08}$ &$10.93\substack{+0.13\\-0.12}$\\[3pt]
LID360 & $3.918$ & $18\%\pm2\%$ & $0\farcs{}63\pm0\farcs{}02$ & $0.8\pm0.4$ & $21.46\substack{+0.14\\-0.12}$ & $4.914$ & $4\%\pm1\%$ & $23.25\substack{+0.17\\-0.15}$ & $11.17\substack{+0.06\\-0.05}$ &$10.88\substack{+0.11\\-0.11}$\\[3pt]
XID2138 & $1.597$ & $39\%\pm6\%$ & $0\farcs{}50\pm0\farcs{}03$ & $1.2\pm0.4$ & $21.87\substack{+0.17\\-0.15}$ & $2.731$ & $5\%\pm1\%$ & $23.90\substack{+0.31\\-0.24}$ & $10.98\substack{+0.07\\-0.06}$ &$10.70\substack{+0.12\\-0.12}$\\[3pt]
XID2202 & $3.23$ & $33\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $4.0\pm1.0$ & $21.16\substack{+0.30\\-0.24}$ & $3.852$ & $8\%\pm2\%$ & $22.59\substack{+0.29\\-0.23}$ & $11.24\substack{+0.12\\-0.10}$ &$10.96\substack{+0.16\\-0.14}$\\[3pt]
XID2396 & $3.669$ & $24\%\pm11\%$ & $0\farcs{}58\pm0\farcs{}09$ & $0.8\pm1.4$ & $21.40\substack{+0.65\\-0.40}$ & $5.346$ & $2\%\pm1\%$ & $23.36\substack{+0.24\\-0.20}$ & $11.20\substack{+0.26\\-0.16}$ &$10.92\substack{+0.28\\-0.19}$\\[3pt]
CDFS-1 & $1.358$ & $65\%\pm20\%$ & $0\farcs{}14\pm0\farcs{}07$ & $4.8\pm1.1$ & $22.47\substack{+0.40\\-0.29}$ & ... & ... & ... & $10.80\substack{+0.16\\-0.12}$ &$10.52\substack{+0.19\\-0.15}$\\[3pt]
CDFS-229 & $4.329$ & $18\%\pm2\%$ & $0\farcs{}51\pm0\farcs{}03$ & $0.5\pm0.2$ & $21.57\substack{+0.14\\-0.13}$ & ... & ... & ... & $10.98\substack{+0.06\\-0.05}$ &$10.70\substack{+0.12\\-0.11}$\\[3pt]
CDFS-321 & $3.998$ & $25\%\pm12\%$ & $0\farcs{}38\pm0\farcs{}12$ & $2.3\pm2.0$ & $20.34\substack{+0.70\\-0.42}$ & ... & ... & ... & $11.61\substack{+0.28\\-0.17}$ &$11.33\substack{+0.30\\-0.20}$\\[3pt]
CDFS-724 & $1.355$ & $35\%\pm15\%$ & $0\farcs{}12\pm0\farcs{}03$ & $1.6\pm1.1$ & $23.70\substack{+0.58\\-0.38}$ & ... & ... & ... & $10.14\substack{+0.23\\-0.15}$ &$9.86\substack{+0.25\\-0.18}$\\[3pt]
ECDFS-358 & $2.012$ & $56\%\pm14\%$ & $0\farcs{}36\pm0\farcs{}04$ & $1.7\pm0.5$ & $21.34\substack{+0.30\\-0.24}$ & ... & ... & ... & $11.25\substack{+0.12\\-0.10}$ &$10.97\substack{+0.16\\-0.14}$\\[3pt]
SXDS-X1136 & $1.937$ & $41\%\pm8\%$ & $0\farcs{}10\pm0\farcs{}00$ & $2.0\pm0.5$ & $21.92\substack{+0.23\\-0.19}$ & ... & ... & ... & $10.84\substack{+0.09\\-0.08}$ &$10.56\substack{+0.14\\-0.13}$\\[3pt]
SXDS-X50 & $1.423$ & $41\%\pm9\%$ & $0\farcs{}19\pm0\farcs{}04$ & $1.7\pm0.6$ & $21.99\substack{+0.27\\-0.21}$ & ... & ... & ... & $10.89\substack{+0.11\\-0.09}$ &$10.61\substack{+0.15\\-0.13}$\\[3pt]
SXDS-X717 & $1.426$ & $61\%\pm9\%$ & $0\farcs{}26\pm0\farcs{}07$ & $5.6\pm1.4$ & $21.76\substack{+0.18\\-0.15}$ & ... & ... & ... & $10.86\substack{+0.07\\-0.06}$ &$10.58\substack{+0.12\\-0.12}$\\[3pt]
SXDS-X735 & $2.203$ & $32\%\pm9\%$ & $0\farcs{}22\pm0\farcs{}06$ & $2.0\pm1.0$ & $20.92\substack{+0.33\\-0.25}$ & ... & ... & ... & $11.28\substack{+0.13\\-0.10}$ &$11.00\substack{+0.17\\-0.14}$\\[3pt]
SXDS-X763 & $2.376$ & $6\%\pm4\%$ & $0\farcs{}69\pm0\farcs{}53$ & $2.4\pm0.8$ & $24.13\substack{+1.17\\-0.55}$ & ... & ... & ... & $10.03\substack{+0.47\\-0.22}$ &$9.75\substack{+0.48\\-0.24}$\\[3pt]
SXDS-X969 & $1.613$ & $29\%\pm11\%$ & $0\farcs{}11\pm0\farcs{}02$ & $2.1\pm1.1$ & $21.59\substack{+0.52\\-0.35}$ & ... & ... & ... & $11.12\substack{+0.21\\-0.14}$ &$10.83\substack{+0.23\\-0.17}$\\[3pt]

@@

\begin{figure*}
\centering
{
\includegraphics[height=0.35\textwidth]{fig/hist_compare.pdf}
}
\caption{\label{fig:hist_compare} 
Comparison of the histogram of the inferred host flux ratio, based on the different volum of the top-ranked PSFs.}
\end{figure*}

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-L_ev.pdf}}\\
\end{tabular}
\caption{\label{fig:ML} 
Illustration of observed (left) and evolution-corrected (right) correlations between \mbh-\lhost, with local linear relation indicated.  The redshift are color-coded, for distant and intermediate AGNs.
}
\end{figure*}

\begin{figure}
\centering
{
\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}
}
\caption{\label{fig:ML-vz} 
Illustration of the offset in log\mbh\ (VS. $L_R$) as a function of redshift. The orange band is the intrinsic scatter of local linear relation.}
\end{figure}

\begin{figure}
\centering
{
\includegraphics[height=0.4\textwidth]{fig/MBH-Mstar.pdf}
}
\caption{\label{fig:MM} 
Similar to the Figure~\ref{fig:ML}, but the comparison of the \mbh-\smass\ relations.}
\end{figure}
